---
title: "Month 1 Week 2 Practice Answer"
date: "10/6/2017"
output: html_document
---

```{r setup, include=FALSE}
set.seed(50793)
if(!require(pacman)){
  install.packages("pacman")
}
p_load(tidyr)
p_load(dplyr)
p_load(ggplot2)
p_load(tibble)
p_load(readr)
p_load(knitr)

library(tidyr)
library(ggplot2)
library(dplyr)
library(tibble)
library(readr)
library(knitr)

opts_knit$set(root.dir = "~/Documents/Homegrown/Friday_Breakout_Exercises/Month_1/Week_2")


```

## Bring in the data

I use the function read_csv() to assign the data to a new variable called raw_data of type tibble.
```{r read the csv, message=FALSE}
raw_data <- read_csv("Month1_Week2_PracticeData.csv")
```

## Clean the Data
Next I want to clean up the data.  I know all I'm interested in graphing is number of calls, orders, and green attachments based on the date so I will select to keep only those columns.  Next I notice that each row is an individual call but I want to look at my data by date so I **group_by()** TheDate.  Once my data is grouped by the date I want to find the sum of each event for that date so I use the  **summarise_all()** to do so, telling the function to use **sum()** as the aggregation function. Finally since I know that Orders, Calls, and GreenAttachments aren't features, I need to use gather to shrink my data set down to three columns.

```{r cleaning data}
clean_data <- raw_data %>% 
  select(TheDate, Calls, Orders, GreenAttachments) %>%
    group_by(TheDate) %>%
      summarise_all(funs(sum)) %>%
        gather("event", "value", Calls, Orders, GreenAttachments)
```

Now we should be ready to plot, right?  Well let me take one more quick ook at my data first:

```{r last look}
str(clean_data)
```

It appears TheDate is stored as a character data type and not a date.  Let's fix that:

```{r fix the date}
clean_data <- raw_data %>% 
  select(TheDate, Calls, Orders, GreenAttachments) %>%
    group_by(TheDate) %>%
      summarise_all(funs(sum)) %>%
        gather("event", "value", Calls, Orders, GreenAttachments) %>%
          mutate(TheDate = as.Date(TheDate, format = "%m/%d/%y"))
```

## Graph the Data
Now I'm ready to graph.

```{r graph the data}
ggplot(data = clean_data, aes(TheDate, value, color = event)) + geom_line()
```


And there we have it, what a nice looking graph.