---
title: 'Getting and Cleaning Data: Week 3 Example -- EXERCISES'
output:
  html_document:
    df_print: paged
---

## Reading in Data with rvdata
Use the provided code to pull data from the rv_example_query.sql file using rvdata. (No need to change anything other than the path to your query file if you choose this route) 
If your connection to rvdata is not working, read in the data from the rv_example_data.csv file. (Write your own code and skip the code provided in the chunk below)
```{r}
queryFile <- '~/Documents/dsc-homegrown/w3_breakout/rv_example_query.sql'
atlasConn <- rvdata::getAtlasDatabaseConnection(company = 'VZ')
dbData <- rvdata::pullDbData(queryFile = queryFile, dbType = 'MSSQL', conn = atlasConn)
```

This data contains marketing events (site visits) and orders. Each row is a marketing event. The rightmost columns specify whether the marketing event
was the "last touch" a customer visited before ordering, the "first touch" a customer visited before ordering. Linear splits orders across all
the events that led to it. For example, if a customer had 2 marketing events, the "Linear" column appears as 0.5 for each event (row). If a customer
had 4 marketing events, the "Linear" column contains 0.25 for each event (row).

The TotalTouchpoints column indicates how many marketing events are associated with the order (i.e. 2 visits, 4 visits, 1 visits).

## Data Manipulation with dplyr
1. Restrict to rows where TotalTouchpoints > 1 and OrderCompany is either 73 or 54 (Frontier or Verizon).
2. Calculate the number of first touch, last touch, and linear orders associated with each EventType and Brand.

First touch orders is defined as the sum of the FirstTouch column.
Last touch orders is defined as the sum of the LastTouch column.
Linear orders is defined as the sum of the Linear column. This could be non-integer number. 
```{r}

```
## String manipulation
1. Glimpse at the data to get an understanding of what you are starting with.
```{r}

```
2. Use lubridate to change the order timestamps into a useable format.
3. Create a column that identifies an RLSA event. RLSA events are defined as any row where the CampaignName contains the pattern 'RLSA'.
4. Remove 'Control' and 'Experiment' words from the CampaignName (replace them with an empty string) in order to clean up this column.
5. Calculate the number of RLSA events for each EventCompany (not OrderCompany)
6. Bonus: For each EventCompany, calculate the number of unique CampaignNames once Control and Experiment are removed in step 4.
```{r}

```
## Plotting
Optional: Use the skills learned in week 2 to plot this data in ggplot.
```{r}

```

